Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-25 draft/ms_v4.tex
More edits

    \noindent Synthetic objects can be one of the following:

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Compare with the behaviours of the Kron photometry for galaxies
%\begin{figure*}
%    \begin{center}
%        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_kron}
%    \end{center}
%    \caption{
%        Basic performance of the Kron photometry for synthetic galaxies.
%        \textbf{Left} shows the accuracy in $i$-band.
%        magnitude. The format is identical to Fig \ref{fig:galaxy_mag}.
%        \textbf{Right} shows the accuracy of the $(g-i)$ color using
%        Kron photometry.
%        Other formats are identical to Fig \ref{fig:cmodel_color}.
%        }
%    \label{fig:galaxy_kron}
%\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    In this section, we briefly discuss a few other  \hscpipe{} aspects that relate
    to astrometric calibration, star-galaxy separation, blendedness and photometric errors, and galaxy shape measurements to demonstrate the range of topics that can be tested with \synpipe{}.

@@

    For a \synpipe{} test, we inject synthetic objects to single-\visit{} images using
    the less accurate initial astrometric calibration.
    During the image stacking step, the joint calibration process  improves the
    astrometric solutions.
    Therefore, the differences between the input and output coordinates from \synpipe{}
    can help us understand the systematic effect of the image stacking step.

@@

%% ------------------------------------------------------------------------------------ %%
%\subsection{Comparing to Kron photometry}

%    \plan{Uses $i$-band as example to briefly discuss Kron photometry}

%    \plan{Although magnitude for galaxies is Ok, the color becomes worse}

@@

    We also notice a few issues in the current \hscpipe{}:

@@

    %% Future developments
    Both \hscpipe{} and \synpipe{} are currently undergoing active development. The plan is to update \synpipe{} to provide a photometric benchmark for
    each HSC survey data release, which will help \hscpipe{} improve.
    At the same time, we are also working on improving the efficiency of \synpipe{}.
    Since many survey data users are not concerned with the subtle effects involved in the image stacking process, we will update \synpipe{} so that it can directly inject synthetic objects to the \coadd{} images and speed up these tests.

>>>>

    \vspace{0.5cm}
    \noindent Synthetic objects can be one of the following:

@@

@@

    In this section, we briefly discuss a few other \hscpipe{} aspects that relate
    to astrometric calibration, star-galaxy separation, blendedness and photometric 
    errors, and galaxy shape measurements to demonstrate the range of topics \synpipe{}
    can test.

@@

    For \synpipe{} test, we inject synthetic objects to single-\visit{} images using
    the less accurate initial astrometric calibration.
    During the image stacking step, the joint calibration process improves the
    astrometric solutions.
    Therefore, the differences between the input and output coordinates from \synpipe{}
    can help us understand the systematic effect of the image stacking step.

@@

@@

    \vspace{0.5cm}
    \noindent We also notice a few issues in the current \hscpipe{}:

@@

    %% Future developments
    Both \hscpipe{} and \synpipe{} are undergoing active development. 
    Our plan is to update \synpipe{} to provide a photometric benchmark for
    each HSC survey data release, which will help \hscpipe{} improve.
    At the same time, we are also working on improving the efficiency of \synpipe{}.
    Since many survey data users are not concerned with the subtle effects involved in 
    the image stacking process, we will update \synpipe{} so that it can directly 
    inject synthetic objects to the \coadd{} images and speed up these tests.
